\begin{abstract}
Kinase inhibitor selectivity is routinely quantified using one of several
definitions --- including the S-score, selectivity entropy, Gini coefficient,
and ratio-based measures --- yet these definitions are applied interchangeably
without systematic justification.
We characterize, across two large kinase inhibitor profiling datasets
(Davis, $n=68$; Klaeger, $n=222$), the extent and structural sources of
disagreement between definitions as their parameters vary.
Spearman correlations between median rankings reveal that ratio-based
definitions cluster separately from entropy- and distribution-based definitions
($r = 0.27$--$0.48$ vs.\ $r = 0.75$--$0.91$).
Rank instability is not random: three mechanistically distinct sources are
identified.
Drugs with no detected binding above a minimum affinity threshold exhibit
maximal instability (mean rank $\sigma \approx 74$) due to definitional noise.
Among active compounds, near-tied top targets drive ratio-specific instability
($r = -0.293$, $p < 0.001$), while broad flat binding profiles drive
instability within distribution-based families.
Attempts to correlate selectivity scores with clinical adverse event rates
from FAERS ($n=46$) and FDA label discontinuation rates ($n=33$) yield null
results, which we attribute to confounding by indication severity and
prescription volume.
From these findings we derive four desiderata toward a well-formed selectivity
measure: a reliability threshold condition, bounded gap sensitivity,
distributional consistency under parameter perturbation, and monotonicity
under weak off-target addition.
These desiderata are intended as the empirical foundation for a future formal
axiomatization, in the tradition of Shannon's characterization of entropy.
\end{abstract}
