\section{Desiderata for a Well-Formed Selectivity Measure}
\label{sec:desiderata}

The empirical findings of the Results section motivate four properties
that any well-formed kinase inhibitor selectivity measure should satisfy.
We present these as desiderata rather than axioms: they are necessary
conditions motivated by observed failure modes of existing definitions, but
they are not yet proven to be jointly sufficient to characterize a unique
measure, nor is it known whether they are jointly satisfiable.
Establishing these properties formally is the subject of future work.

Let $\mathbf{x} = (x_1, \ldots, x_N) \in \mathbb{R}^N$ denote a compound's
binding profile across $N$ kinases, where $x_i = \mathrm{p}K_{d,i}$.
A selectivity measure is a function $f : \mathbb{R}^N \to \mathbb{R}$, where
higher values indicate greater selectivity.
A selectivity ranking over a set of compounds is induced by ordering their
$f$-scores.

\paragraph{D1 --- Reliability threshold.}
There exists a threshold $\tau^* > 0$ such that $f(\mathbf{x})$ is undefined,
or explicitly flagged as unreliable, when $\max_i x_i \leq \tau^*$.

\textit{Motivation.}
Compounds with no detected binding above the assay detection floor receive
arbitrary selectivity scores under all four definitions studied here, producing
rank instability with mean $\sigma \approx 74$ compared with $\sigma \approx
32$ for active compounds (Type~1 instability, above).
Selectivity is a property of binding; a compound that does not bind cannot be
meaningfully ranked relative to compounds that do.
No existing definition incorporates an explicit reliability condition: both
the S-score and selectivity entropy assign scores to compounds with no
sub-micromolar binding, treating detection floor values as informative.

\paragraph{D2 --- Bounded gap sensitivity.}
For any compound profile $\mathbf{x}$ satisfying D1, a small perturbation to
the identity of the reference off-target should produce a bounded change in
$f(\mathbf{x})$.
Formally, if $f$ depends on the $k$-th ranked affinity $x_{(k)}$, then
$|f(\mathbf{x}; k) - f(\mathbf{x}; k+1)|$ should be bounded by a function of
$x_{(k)} - x_{(k+1)}$.

\textit{Motivation.}
Ratio-based definitions violate this property when $x_{(1)} \approx x_{(2)}$:
a compound with near-identical affinities for its top two kinases receives a
large ratio score when $k=1$ (the gap to the next off-target may be large) but
a near-zero score when $k=2$ (the gap between the tied targets is negligible).
This produces the Type~2 instability identified in
the instability taxonomy above, where top$_1$--top$_2$ gap is the
strongest predictor of ratio instability ($r = -0.293$, $p < 0.001$).
Distribution-based definitions (entropy, Gini) satisfy a weaker version of
this property because they do not privilege any single pairwise comparison.

\paragraph{D3 --- Distributional consistency.}
The ranking induced by $f$ should be stable under small perturbations to the
activity baseline $\beta$ used to define the active binding distribution.
Formally, for any two compounds $\mathbf{x}, \mathbf{y}$ and any
$\epsilon > 0$, there exists $\delta > 0$ such that if $|\beta_1 - \beta_2|
< \delta$ then the ranking of $\mathbf{x}$ relative to $\mathbf{y}$ under
$f(\cdot; \beta_1)$ agrees with that under $f(\cdot; \beta_2)$.

\textit{Motivation.}
The entropy and Gini definitions are parameterized by a baseline $\beta$ that
determines which affinities contribute to the binding distribution.
Compounds with few active kinases are sensitive to this choice because small
changes in $\beta$ can move individual kinases in or out of the active set,
substantially altering the distribution.
The negative correlation between $n_\mathrm{active}$ and entropy/Gini
instability ($r = -0.47$ on Klaeger, $p < 0.001$) reflects this sensitivity.
D3 requires that the ranking be robust to the choice of $\beta$ within a
reasonable neighborhood, which existing implementations do not guarantee.

\paragraph{D4 --- Monotonicity under weak off-target addition.}
If compound $\mathbf{x}$ has a weak additional binding interaction added ---
formally, if $\mathbf{x}' = (x_1, \ldots, x_N, x_{N+1})$ where $x_{N+1} \leq
\tau^*$ --- then $f(\mathbf{x}') \leq f(\mathbf{x})$.
Adding a sub-threshold binding interaction should not increase a compound's
selectivity score.

\textit{Motivation.}
Ratio-based definitions can violate this property: if the new weak interaction
becomes the reference off-target ($k=1$), the ratio to the primary target may
increase, artifactually improving the apparent selectivity score.
This failure mode is practically relevant when profiling panels differ in size
or composition across experiments, as is common when comparing selectivity
across different assay platforms or across datasets such as Davis and Klaeger.
Distribution-based definitions satisfy D4 naturally, since adding a
sub-threshold term to the probability distribution decreases or preserves
entropy and Gini.

\bigskip
Table~\ref{tab:desiderata} summarizes which existing definitions satisfy each
desideratum.
No existing definition satisfies all four simultaneously.
Whether a definition satisfying all four exists, and whether the four desiderata
are jointly consistent, are open questions that we identify as the primary
targets of a formal axiomatization.

\begin{table}[h]
  \centering
  \caption{Satisfaction of desiderata by existing selectivity definitions.
           $\checkmark$: satisfied by construction.
           $\sim$: partially satisfied or satisfied under additional assumptions.
           $\times$: violated in general.}
  \label{tab:desiderata}
  \begin{tabular}{lcccc}
    \toprule
    Desideratum & S-score & Entropy & Gini & Ratio \\
    \midrule
    D1 (reliability threshold)        & $\times$ & $\times$ & $\times$ & $\times$ \\
    D2 (bounded gap sensitivity)      & $\sim$   & $\checkmark$ & $\checkmark$ & $\times$ \\
    D3 (distributional consistency)   & $\sim$   & $\times$ & $\times$ & $\checkmark$ \\
    D4 (monotonicity, weak off-target)& $\checkmark$ & $\checkmark$ & $\checkmark$ & $\times$ \\
    \bottomrule
  \end{tabular}
\end{table}
