\section{Discussion}
\label{sec:discussion}

The central finding of this work is that existing kinase inhibitor selectivity
definitions do not measure the same quantity.
The ratio definition and the distribution-based family (S-score, entropy, Gini)
produce substantially different compound rankings ($r = 0.27$--$0.48$),
and the sources of disagreement are mechanistically interpretable rather than
random.
This has practical consequences: a compound that ratio-based analysis designates
as selective may be designated as moderately promiscuous by entropy-based
analysis, and vice versa, depending on the shape of its binding profile.
Go/no-go decisions in early drug discovery are routinely made on the basis of
selectivity assessments without acknowledgment that the choice of definition
materially affects the outcome.

\subsection{The Two-Family Structure Reflects a Conceptual Distinction}

The clustering of definitions into two families is not a statistical artifact
but reflects a genuine difference in what is being measured.
Distribution-based definitions ask: how concentrated is the compound's binding
activity across the full profiled kinome?
The ratio definition asks: how much more potently does the compound bind its
primary target than a specified off-target?
These are distinct questions with distinct answers for a large class of
compounds --- specifically, those with one clearly dominant target that also
bind many kinases at moderate affinity (Type~3 profiles in our taxonomy).
For such compounds, ratio-based methods report high selectivity while
distribution-based methods report moderate promiscuity, and both
characterizations are correct given their respective questions.

The disagreement is therefore not a defect to be corrected by choosing the
``right'' definition, but a signal that the field has not agreed on what
selectivity means.
The desiderata proposed in Section~\ref{sec:desiderata} are an attempt to make
this question precise enough that it can be answered formally.

\subsection{The Historical Roots of Definitional Ambiguity}

The coexistence of ratio-based and distribution-based selectivity definitions
in the kinase inhibitor literature has a historical explanation rooted in the
structure of the selectivity question itself.
In classical pharmacology and analytical chemistry, selectivity is inherently
pairwise: how much more potently does a compound bind target A than target B?
IUPAC formalizes this for analytical methods as a selectivity coefficient ---
the ratio of binding constants for analyte and interferent --- and organic
chemistry quantifies chemo-, regio-, and stereoselectivity as ratios of
competing rate constants.\cite{IUPAC2001}
These ratio definitions are appropriate because the question is binary.

Kinase inhibitor selectivity, by contrast, is a distributional question: how
concentrated is a compound's binding activity across a panel of hundreds of
kinases?
This is structurally different from a pairwise comparison, and ratio-based
measures are poorly suited to it precisely because they discard all but two
data points from a profile of 300--500 kinases, as the panel size analysis of
Section~\ref{sec:results:panelsize} makes quantitative.
The entropy and Gini definitions were introduced specifically because
researchers recognized that ratio measures were inadequate for large panels,
but the older definitions were never retired.
The result is a field that applies pairwise measures to distributional
questions and distributional measures to pairwise questions, without a
principled basis for choosing between them.
The desiderata of Section~\ref{sec:desiderata} can be understood as an attempt
to make this distinction precise: D2 (bounded gap sensitivity) and D4
(monotonicity) are properties that ratio definitions violate specifically
because they treat a distributional problem as pairwise, while D3
(distributional consistency) is a property that ratio definitions satisfy
trivially because they do not use a distributional baseline at all.

\subsection{Practical Recommendations}

Pending a formal resolution, three practical recommendations follow from our
findings.

First, D1 (reliability threshold) should be adopted immediately as a reporting
standard.
Compounds with no detected binding above the assay detection floor should not
receive selectivity scores, or should have their scores explicitly flagged as
unreliable.
Of the 222 Klaeger compounds, 16 (7.2\%) fall into this category and currently
receive scores that are indistinguishable from noise.

Second, selectivity assessments should report the sensitivity of rankings to
parameter choice rather than a single score at a single parameter value.
Our analysis shows that rank standard deviation across the parameter sweep is a
compound-specific, interpretable quantity that identifies which compounds have
robust selectivity assessments and which do not.
This is analogous to reporting confidence intervals in statistical estimation.

Third, when comparing selectivity across studies that use different definitions,
the comparison should be restricted to the subset of compounds and parameter
values for which the definitions agree.
The high within-family correlations ($r > 0.74$) suggest that S-score, entropy,
and Gini are interchangeable for most purposes when parameters are chosen
consistently; ratio-based measures should not be compared directly with
distribution-based measures without acknowledging the conceptual distinction.

\subsection{Limitations}

The analysis is limited to two profiling datasets that, while large and
well-characterized, represent a small fraction of the chemical and kinase space
relevant to drug discovery.
Davis covers 68 compounds and 433 kinases using a fixed-concentration
competition binding assay; Klaeger covers 222 clinical compounds and 343
kinases using chemoproteomic dose--response profiling.
The two assay technologies are not directly comparable, and the difference in
active compound fractions (17.9\% for Davis vs.\ 3.6\% for Klaeger) reflects
both genuine selectivity differences and assay-specific detection thresholds.
Findings should be interpreted in light of these technological differences.

The clinical outcome analysis is limited by the observational nature of FAERS
data and the heterogeneity of FDA label discontinuation rates across indications.
The null results reported in Section~\ref{sec:results:outcomes} are consistent
with a genuine absence of correlation between in vitro selectivity and clinical
toxicity, but they are equally consistent with the confounders identified
therein.
A properly controlled study would require prospective collection of
treatment-related adverse event rates stratified by indication, which is not
currently available in a standardized form across the breadth of approved
kinase inhibitors.

The desiderata proposed in Section~\ref{sec:desiderata} are necessary
conditions motivated by empirical failure modes; they are not proven to be
sufficient to uniquely characterize a selectivity measure, and it is not known
whether they are jointly satisfiable.
The satisfaction assessments in Table~\ref{tab:desiderata} are based on
analysis of the functional forms of each definition and the empirical findings
of this study; a formal proof of satisfaction or violation for each
desideratum--definition pair is left for future work.

\subsection{Relation to Formal Methods}

The approach taken here --- characterizing the empirical behavior of competing
definitions to motivate formal desiderata --- follows a methodology well
established in adjacent fields.
Shannon's derivation of entropy began with the observation that several
reasonable-seeming measures of uncertainty existed and proceeded to identify
the axioms that single out one uniquely.\cite{Shannon1948}
Arrow's impossibility theorem began with the observation that several
reasonable voting rules existed and proved that no rule satisfies all
desirable properties simultaneously.\cite{Arrow1951}

The present work occupies the empirical stage of this process: we have
characterized where and why existing definitions disagree, and proposed
properties that any satisfactory definition should have.
Whether a definition satisfying all four desiderata exists, whether the
desiderata are jointly consistent, and whether an impossibility result holds,
are questions for a formal axiomatization.
We anticipate that such an axiomatization, potentially implemented in a proof
assistant such as Agda or Lean, would constitute a natural and
productive extension of this work.\cite{Lean4Mathlib}
