\section{Introduction}
\label{sec:intro}

Kinase inhibitors are among the most intensely investigated compound classes
in drug discovery, with over 80 FDA-approved agents and several hundred in
clinical development.\cite{Roskoski2024}
Because the human kinome comprises more than 500 proteins sharing a
highly conserved ATP-binding site,\cite{Manning2002} the design of inhibitors
with controlled target profiles remains a central challenge.
Selectivity --- the degree to which a compound's binding activity is
concentrated on intended rather than off-target kinases --- is a primary
criterion in lead optimization and a key determinant of the therapeutic window
of approved drugs.\cite{Bhullar2018}

Despite its importance, selectivity is not formally defined.
The field employs at least four distinct quantitative measures:
the S-score,\cite{Karaman2008} selectivity entropy,\cite{Uitdehaag2011}
Gini coefficient,\cite{Graczyk2010} and ratio-based measures including the
CATDS score.\cite{Klaeger2017}
These definitions are applied interchangeably in the literature without
systematic justification, and their parameter values --- the activity threshold
in the S-score, the baseline in the entropy and Gini coefficient, the reference
off-target in ratio-based measures --- are chosen by convention rather than
principle.
Bosc et al.\cite{Bosc2017} showed that these definitions can produce
substantially different compound rankings on the same dataset, and the
KInhibition platform\cite{KInhibition2018} explicitly acknowledged that
conflicting results across metrics are common.
However, the structural sources of this disagreement --- which binding profile
properties determine when definitions agree or conflict, and why --- have not
been characterized.

The absence of a principled basis for selectivity measurement is not merely
a practical inconvenience.
Go/no-go decisions worth hundreds of millions of dollars in development costs
are made on the basis of selectivity assessments whose sensitivity to
definitional choice is unknown.
When a compound is described as ``selective'' in the literature, the claim is
implicitly conditioned on a specific definition and parameterization that is
rarely stated explicitly and almost never justified.
This situation is analogous to measuring temperature with instruments whose
scales have not been calibrated to a common reference: the measurements are
internally consistent but not directly comparable.

The analogy to measurement theory suggests a remedy.
In information theory, Shannon\cite{Shannon1948} resolved the question of how
to measure uncertainty by identifying axioms that uniquely characterize the
entropy functional.
In social choice theory, Arrow\cite{Arrow1951} resolved --- negatively ---
the question of how to aggregate individual rankings by proving that no
aggregation rule can simultaneously satisfy a small set of reasonable
requirements.
In both cases, the path from empirical observation to formal resolution
required first characterizing the behavior of competing approaches and then
identifying the properties that distinguish good measures from bad ones.

This paper takes the first step of that program for kinase inhibitor
selectivity.
We systematically characterize, across two large profiling datasets, the
extent and structural sources of disagreement between existing definitions as
their parameters vary.
We identify three mechanistically distinct sources of rank instability and show
that instability is predictable from the shape of a compound's binding profile.
We then propose four desiderata --- necessary properties of any well-formed
selectivity measure --- motivated directly by these failure modes.

Specifically, the contributions of this work are as follows.
First, we show that existing definitions cluster into two families ---
distribution-based (S-score, entropy, Gini) and ratio-based (CATDS and
variants) --- that correlate poorly with one another ($r = 0.27$--$0.48$)
and measure fundamentally different properties of binding profiles.
Second, we identify three sources of instability: definitional noise for
compounds below the assay detection threshold, ratio-specific instability
driven by near-tied top targets, and distribution-ratio disagreement for
compounds with one dominant target and broad moderate off-target activity.
Third, we propose four desiderata --- a reliability threshold condition,
bounded gap sensitivity, distributional consistency, and monotonicity under
weak off-target addition --- and show that no existing definition satisfies
all four simultaneously.
Fourth, we demonstrate that correlations between selectivity scores and
clinical adverse event outcomes are null under current data sources, and
identify the confounders responsible.

The desiderata proposed here are intended as the empirical foundation for a
future formal axiomatization of kinase inhibitor selectivity, in the tradition
of Shannon's characterization of entropy and Arrow's analysis of social choice
functions.
\end{document}
