\section{Methods}
\label{sec:methods}

\subsection{Datasets}
\label{sec:methods:data}

Two publicly available kinase inhibitor profiling datasets were used.
The Davis dataset\cite{Davis2011} comprises binding affinities ($K_d$) for 68
small-molecule kinase inhibitors measured against 433 human kinase domains.
Affinity values are reported as dissociation constants and were converted to
$\mathrm{p}K_d = -\log_{10}(K_d / 10^9)$ prior to analysis, following the
convention of the DeepDTA benchmark.\cite{DeepDTA}
Pairs for which no binding was detected at the screening concentration of
10~$\mu$M were assigned $\mathrm{p}K_d = 5.0$, corresponding to a $K_d$ of
1~mM, which represents the detection floor of the assay.
The resulting affinity matrix is complete ($68 \times 433$, 29{,}444 entries).
No censored or greater-than values are present in the Davis dataset: the assay
reports a quantitative $K_d$ for every compound--kinase pair where activity was
detected at 10~$\mu$M, and assigns the detection floor value otherwise.
All non-binding pairs are therefore treated as exactly equivalent at
$\mathrm{p}K_d = 5.0$, which slightly underestimates true non-binding affinity
but is the standard convention for this dataset.\cite{DeepDTA,Bosc2017}

The Klaeger dataset\cite{Klaeger2017} comprises binding affinities for 243
clinical kinase inhibitors profiled against the human kinome using
Kinobeads chemical proteomics.
Apparent dissociation constants ($K_d^\mathrm{app}$) were derived from
dose--response curves across eight inhibitor concentrations in cancer cell
lysates.
Only high-confidence measurements (as annotated by the original authors) were
retained, yielding 5{,}123 drug--target pairs for 222 drugs and 343 kinase
targets.
Affinity values were converted to $\mathrm{p}K_d$ using the same formula as
above.
Missing entries, representing kinase--inhibitor combinations not detected in
the assay, were assigned the background value $\mathrm{p}K_d = 5.0$.
The resulting matrix ($222 \times 343$) has 17.9\% active entries
(pKd $> 6$, i.e.\ $K_d < 1~\mu$M) for Davis and 3.6\% for Klaeger,
reflecting the more stringent detection threshold of the chemoproteomic assay.

\subsection{Selectivity Definitions and Parameterization}
\label{sec:methods:defs}

Four selectivity definitions were implemented, each controlled by one or more
parameters whose values are not standardized in the literature.

The \textbf{S-score}\cite{Karaman2008} is defined as
\begin{equation}
  S(\tau) = \frac{1}{N} \sum_{i=1}^{N} \mathbf{1}[\mathrm{p}K_{d,i} > \tau],
\end{equation}
where $N$ is the number of kinases in the panel and $\tau$ is an activity
threshold.
Lower values indicate greater selectivity.
We swept $\tau \in \{5.5, 5.75, \ldots, 8.0\}$ (11 values), spanning $K_d$
cutoffs from approximately 300~nM to 10~nM.

The \textbf{selectivity entropy}\cite{Uitdehaag2011} treats the
baseline-subtracted binding profile as a probability distribution:
\begin{equation}
  H(\beta) = -\sum_{i=1}^{N} p_i \log_2 p_i, \quad
  p_i = \frac{\max(\mathrm{p}K_{d,i} - \beta,\, 0)}
             {\sum_j \max(\mathrm{p}K_{d,j} - \beta,\, 0)},
\end{equation}
where $\beta$ is a baseline affinity below which binding is considered
negligible.
Lower entropy indicates greater selectivity.
We swept $\beta \in \{5.0, 5.25, \ldots, 6.5\}$ (7 values).

The \textbf{Gini coefficient}\cite{Graczyk2010} of the baseline-subtracted
profile is
\begin{equation}
  G(\beta) = \frac{2\sum_{i=1}^{N} i \cdot x_{(i)}}{N \sum_{i=1}^{N} x_{(i)}} - \frac{N+1}{N},
\end{equation}
where $x_{(i)} = \max(\mathrm{p}K_{d,i} - \beta,\, 0)$ sorted in ascending
order.
Higher values indicate greater selectivity.
We swept $\beta$ over the same range as for the entropy.

The \textbf{ratio} definition measures the gap between the primary target and
a specified off-target:
\begin{equation}
  R(k) = \mathrm{p}K_{d,(1)} - \mathrm{p}K_{d,(k+1)},
\end{equation}
where $\mathrm{p}K_{d,(j)}$ denotes the $j$-th largest affinity in the profile
and $k \in \{1, 2, 3, 4, 5\}$ indexes the off-target used as reference.
Higher values indicate greater selectivity.

\subsection{Rank Stability Analysis}
\label{sec:methods:stability}

For each definition and each parameter value, compounds were ranked from most
selective (rank 1) to least selective (rank $n$, where $n$ is the number of
compounds in the dataset).
Ties were broken by average rank.
This yielded 30 rank vectors per dataset: 11 for the S-score, 7 for entropy,
7 for Gini, and 5 for ratio.

For each compound, rank instability was quantified as the standard deviation
of its rank across all 30 configurations (overall instability) and separately
across configurations within each definition family (within-family
instability).
Cross-definition agreement was assessed using Spearman rank correlation
between the median rank vectors of each definition family.
The median was taken across parameter values within each family prior to
correlation to obtain a single representative ranking per definition.

Associations between rank instability and binding profile features were
assessed using Spearman correlation.
Profile features computed for each compound included: the number of active
kinases ($\mathrm{p}K_d > 6$), the gap between the top and second-ranked
affinities, the standard deviation and range of active affinities, and the
absolute affinity of the second-ranked target.
All correlations are reported with two-tailed $p$-values; significance
thresholds of $p < 0.05$, $p < 0.01$, and $p < 0.001$ are denoted *, **, and
*** respectively.
Analyses were performed in Python 3.10 using NumPy, pandas, and
SciPy.\cite{NumPy,pandas,SciPy}

\subsection{Clinical Outcome Data}
\label{sec:methods:outcomes}

For the subset of Klaeger compounds that are FDA-approved ($n = 46$ after
excluding drugs with no FAERS records), adverse event report counts were
retrieved from the FDA Adverse Event Reporting System (FAERS) via the
openFDA API.
Total report counts, serious event counts, and death and hospitalization
subcounts were retrieved per drug.
Serious event rates and death rates were computed by normalizing subcounts by
total reports per drug.

Treatment discontinuation rates due to adverse events were extracted from FDA
drug labels retrieved via the openFDA label API for 33 approved drugs with
available adverse reactions sections.
Label text was reviewed manually to identify the primary clinical trial
discontinuation rate attributable to adverse reactions.

Associations between selectivity scores and each clinical outcome measure were
assessed using Spearman correlation across drugs with available data.
