\section{Related Work}
\label{sec:related}

\subsection{Existing Selectivity Metrics and Their Comparison}
\label{sec:related:metrics}

Several metrics have been proposed to quantify kinase inhibitor selectivity
from profiling panel data.
Karaman et al.\cite{Karaman2008} introduced the selectivity score (S-score),
defined as the fraction of panel kinases inhibited above a fixed concentration
threshold.
Uitdehaag and Zaman\cite{Uitdehaag2011} proposed the selectivity entropy,
which treats the normalized binding profile as a probability distribution and
computes its Shannon entropy; low entropy indicates activity concentrated on
few targets.
Graczyk\cite{Graczyk2010} defined a thermodynamics-based partition index
estimating the fraction of total binding directed to a reference kinase,
suited primarily to hit-to-lead optimization against a specified target.
Klaeger et al.\cite{Klaeger2017} introduced the concentration- and
target-dependent selectivity (CATDS) score, which quantifies the reduction in
binding to a given target relative to the summed reduction across all detected
targets at a specified inhibitor concentration.
Bosc et al.\cite{Bosc2017} subsequently proposed two further metrics ---
the window score and ranking score --- and performed a comparative analysis of
all five definitions on the Davis and Anastassiadis datasets, showing that
compound rankings differ substantially depending on the metric applied and that
certain compounds cannot be scored under some definitions when threshold
conditions are not satisfied.

Reconciliation attempts have remained limited in scope.
Bajorath et al.\cite{Bajorath2018} compared CATDS-based selectivity
assessments from Klaeger et al.\ with activity data mined from ChEMBL for the
same compounds, finding broad consistency between the two sources but noting
that no simple relationship between selectivity and clinical performance was
apparent.
The KInhibition platform\cite{KInhibition2018} explicitly acknowledged that
multiple metrics yield conflicting results for the same compound but addressed
this through a unified query interface rather than theoretical analysis.

A common limitation of these studies is that each metric is evaluated at fixed
parameter values.
The sensitivity of rankings to parameter choice --- the activity threshold in
the S-score, the baseline in the entropy and Gini coefficient, the reference
off-target in ratio-based measures --- has not been systematically
characterized.
The structural properties of binding profiles that determine when definitions
agree or disagree have not been identified.
The present work addresses both gaps.

\subsection{Axiomatic Approaches to Ranking and Measurement}
\label{sec:related:axiomatic}

Axiomatic characterization of measurement functions is well-established in
adjacent fields.
Shannon\cite{Shannon1948} demonstrated that the entropy of a probability
distribution is uniquely determined, up to a multiplicative constant, by four
requirements: continuity, maximality on the uniform distribution,
expansibility, and additivity over independent subsystems.
Khinchin\cite{Khinchin1957} subsequently strengthened this uniqueness result.
The selectivity entropy of Uitdehaag and Zaman applies the Shannon formula to
normalized binding profiles but provides no analogous axiomatic justification;
it is not known whether it is the unique function satisfying reasonable
selectivity-specific desiderata, or one of many equivalent alternatives.

Arrow\cite{Arrow1951} established that no social welfare function satisfies
simultaneously the requirements of unrestricted domain, Pareto efficiency,
independence of irrelevant alternatives, and non-dictatorship.
The theorem is relevant here in two respects: it demonstrates that axiomatic
analysis of a ranking concept can yield impossibility rather than uniqueness,
and it shows that competing ranking functions reflect genuine tradeoffs between
properties that cannot all be achieved simultaneously.
Pavillidis et al.\cite{Pavillidis2022} applied this methodology to truth
discovery --- the problem of identifying true facts from conflicting reports of
unknown reliability --- posing it as a social choice problem, formulating
candidate axioms, and proving that a subset cannot be jointly satisfied.
The structure of that problem is closely analogous to selectivity measurement,
where multiple definitions produce conflicting rankings and the question of
which to trust is unresolved.

Formal methods have been applied to biological systems primarily in the context
of process dynamics.
Cardelli\cite{Cardelli2004} used the pi-calculus to model molecular biology,
and the Beacon Calculus\cite{Beaconcalculus2019} addresses stochastic reaction
networks; both verify properties of temporal execution rather than static
measurements.
Type-theoretic approaches to scientific units of measure, including
Kennedy's\cite{Kennedy1994} F\# units-of-measure system and ongoing
formalization in Lean~4 Mathlib,\cite{Lean4Mathlib} enforce dimensional
consistency for physical quantities but do not extend to biochemical
properties.
To our knowledge, axiomatic analysis has not previously been applied to any
selectivity or promiscuity measure in drug discovery.
The present work proposes empirically motivated desiderata as a foundation for
future formal axiomatization.
