\documentclass[journal=jcisd8,manuscript=article]{achemso}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{microtype}

\author{Polina Vinogradova}
\affiliation{Input Output Global, Singapore}
\altaffiliation{ORCID: 0000-0003-3271-3841}
\email{polina.vinogradova@iohk.io}

\title{Towards a Formal Definition of Kinase Inhibitor Selectivity:
  Empirical Characterization of Definitional Instability and Proposed Desiderata}

\abbreviations{S-score, CATDS, pKd, FAERS}
\keywords{kinase inhibitor selectivity, selectivity metrics, binding affinity,
  axiomatic analysis, drug discovery, cheminformatics}

\begin{document}

\input{sections/abstract}
\input{sections/introduction}
\input{sections/related_work}
\input{sections/methods}
\input{sections/results}
\input{sections/desiderata}
\input{sections/discussion}
\input{sections/conclusion}

\begin{acknowledgement}
The authors thank the developers of the Davis and Klaeger datasets for making
their data publicly available.
The author used Claude (Anthropic, claude.ai), a large language model assistant,
during the preparation of this manuscript.
Specifically, Claude was used to assist with: data analysis code development and
debugging in Python; literature search and identification of related work;
drafting and editing of manuscript text; and research planning and
interpretation of results.
All scientific conclusions, the conceptual framework, the desiderata proposed in the Desiderata section, 
and the final manuscript content were developed, verified, and approved by the author.
The author takes full responsibility for the accuracy and integrity of all
content in this work.
The use of Claude does not transfer any rights over the content of this manuscript
to Anthropic or any third party.
\end{acknowledgement}

\begin{suppinfo}
A preprint of this manuscript is available on ChemRxiv at
\url{https://doi.org/10.26434/chemrxiv.15001618/v1}.
\end{suppinfo}

\section*{Data and Software Availability}
All data and software used in this study are publicly available.
The Davis kinase inhibitor profiling dataset is available at
\url{https://github.com/dingyan20/Davis-Dataset-for-DTA-Prediction}.
The Klaeger et al.\ dataset is available as supplementary data to the
original publication (Science, 2017, \url{https://doi.org/10.1126/science.aan4368}).
All analysis scripts, processed data files, and the \LaTeX\ source for
this manuscript are available at
\url{https://github.com/polinavino/kinase-selectivity-definitions}.
No confidential data were used in this study.
All results reported in this manuscript are fully reproducible from the
publicly available data and code.

\bibliography{references}

\end{document}
